# Vis–NIR modelling and predictions

------------------------------------------------------------------------

A prediction model based on vis–NIR spectra was fitted for each soil property using the selected optimal calibration subset. Each model was developed using a memory-based learning (MBL) algorithm (from the `resemble` package). Please check the paper for additional details on the MBL lagorithm used (see section _Vis–NIR modelling and predictions_ subsections 1-3). 

## Calibration and validation
First define some basic aspects of the MBL which will be commmon to all the properties for which NIR modeling is going to be performed. 
```{r eval = FALSE}
## Add to the train data a variable indicating to what sampling point
## each sample belongs to. This variable will be used internally 
## by the mbl function during the internal validations. 
train$samplegroup <- substr(train$ID, 2, 100)

## Dissimilarity metric: partial least squares (pls)
dmetric <- "pls"

## Threshold distances to be tested
## Note: the number of threshold distances tested here is large, 
## it could be reduced
diss2test <- seq(0.3, 1.5, by = 0.05)

## Define the minimum and maximum number of neighbors that must be retained
## for each local model.
## Example: If with a given threshold distance only 70 neighbors are
## selected, then the function will be fored to take the especified minimum
## number of neighbors to be included in the model. In this case 120. 
## We also set that the maximum number of neighbors that can be
## included can be all the samples in the calibration set.
kminmax <- c(120, nrow(train$spc))

## Regression method: Weighted average pls (wapls)
rmethod <- "wapls1"

## set the maximum and minimum number of pls factors 
## for the local wapls regressions
pls.f <- c(minpls = 5, maxpls = 20)

## Adjust some additional parameters that control some 
## aspects of the mbl
ctrl <- mblControl(sm = dmetric, 
                   pcSelection = list("opc", 40), 
                   valMethod = "NNv", 
                   returnDiss = TRUE,
                   scaled = FALSE, 
                   center = TRUE)
```

We also create some `data.frames` were we are going to store the prediction results for the validation set
```{r eval = FALSE}
## Create a data frame and store the validation results
## Squared correlation coefficient (R2)
## Root mean squared error (RMSE)
## Mean error (ME)
## (particle size predictions are also back-transformed to the original 
## space to report the R2, RMSE and ME).
valrestuls <- data.frame(Property = c("Ca", 
                                      "alr_clay",
                                      "alr_silt", 
                                      "Clay", 
                                      "Silt",
                                      "Sand"),
                         RMSE = NA,
                         R2 = NA, 
                         ME = NA)

## Create a data frame and store the variance of the residuals for each layer
## (this will be later used for geostatistical analyses)
residualvariances <- data.frame(Property = c("Ca", "alr_Clay", "alr_Silt"),
                                layerA = NA,
                                layerB = NA,
                                layersAB = NA)
```


Now we perfom MBL and predictions for soil exchangeable Ca^2+^:
```{r eval = FALSE}
## Run the MBL and find the optimal threshold distance 
## for neighbor selection and predict Ca for validation
## - MBL fits a wapls model to each sample in Xu using 
##   the calibration samples {Yr,Xr}
## - The internal validation predictions 
##   these are predictions of the nearest samples
##   of each Xu found in Xr - Nearest neighbor validation (NNv) -
sbl_ca <- mbl(Yr = train$Ca ,
              Xr = train$spc,
              Xu = valida$spc,
              mblCtrl = ctrl,
              group = train$samplegroup,
              dissUsage = "none",
              k.diss = diss2test, 
              k.range = kminmax,
              pls.c = pls.f,
              method = rmethod)
sbl_ca

## Best threshold distance
idx.best.ca <- which.min(sbl_ca$nnValStats$st.rmse)
best.kdiss.ca <- sbl_ca$nnValStats$k.diss[idx.best.ca]

## Get the predicted values for the validation set
pred_valCa <- getPredictions(sbl_ca)[,idx.best.ca]

## R2
valrestuls$R2[valrestuls$Property == "Ca"] <- cor(valida$Ca, pred_valCa)^2
# RMSE
valrestuls$RMSE[valrestuls$Property == "Ca"] <- mean((valida$Ca - pred_valCa)^2)^0.5
# ME
valrestuls$ME[valrestuls$Property == "Ca"] <- mean(valida$Ca - pred_valCa)

## Residual variances
## layer A
residualvariances$layerA[residualvariances$Property == "Ca"] <- var(valida$Ca[valida$layer == 'A'] - pred_valCa[valida$layer == 'A'])
## layer B
residualvariances$layerB[residualvariances$Property == "Ca"] <- var(valida$Ca[valida$layer == 'B'] - pred_valCa[valida$layer == 'B'])
## layers A and B
residualvariances$layersAB[residualvariances$Property == "Ca"] <- var(valida$Ca - pred_valCa)
```

MBL and predictions for $alr(clay)$...
```{r eval = FALSE}
sbl_alrclay <- mbl(Yr = train$alr_Clay, 
                   Xr = train$spc, 
                   Xu = valida$spc,
                   mblCtrl = ctrl,
                   group = train$samplegroup,
                   dissUsage = "none",
                   k.diss = diss2test, 
                   k.range = kminmax,
                   pls.c = pls.f,
                   method = rmethod)

## Best threshold distance
idx.best.alrclay <- which.min(sbl_alrclay$nnValStats$st.rmse)
best.kdiss.alrclay <- sbl_alrclay$nnValStats$k.diss[idx.best.alrclay]

## Get the predicted values for the validation set
pred_val_alrclay <- getPredictions(sbl_alrclay)[,idx.best.alrclay]

## R2
valrestuls$R2[valrestuls$Property == "alr_clay"] <- cor(valida$alr_Clay, pred_val_alrclay)^2
# RMSE
valrestuls$RMSE[valrestuls$Property == "alr_clay"] <- mean((valida$alr_Clay - pred_val_alrclay)^2)^0.5
# ME
valrestuls$ME[valrestuls$Property == "alr_clay"] <- mean(valida$alr_Clay - pred_val_alrclay)

## Residual variances
## layer A
residualvariances$layerA[residualvariances$Property == "alr_Clay"] <- var(valida$alr_Clay[valida$layer == 'A'] - pred_val_alrclay[valida$layer == 'A'])
## layer B
residualvariances$layerB[residualvariances$Property == "alr_Clay"] <- var(valida$alr_Clay[valida$layer == 'B'] - pred_val_alrclay[valida$layer == 'B'])
## layers A and B
residualvariances$layersAB[residualvariances$Property == "alr_Clay"] <- var(valida$alr_Clay - pred_val_alrclay)
```

...and $alr(silt)$...
```{r eval = FALSE}
sbl_alrsilt <- mbl(Yr = train$alr_Silt, 
                   Xr = train$spc, 
                   Xu = valida$spc,
                   mblCtrl = ctrl,
                   group = train$samplegroup,
                   dissUsage = "none",
                   k.diss = diss2test, 
                   k.range = kminmax,
                   pls.c = pls.f,
                   method = rmethod)

## Best threshold distance
idx.best.alrsilt <- which.min(sbl_alrsilt$nnValStats$st.rmse)
best.kdiss.alrsilt <- sbl_alrsilt$nnValStats$k.diss[idx.best.alrsilt]

## Get the predicted values for the validation set
pred_val_alrsilt <- getPredictions(sbl_alrsilt)[,idx.best.alrsilt]

## R2
valrestuls$R2[valrestuls$Property == "alr_silt"] <- cor(valida$alr_Clay, pred_val_alrsilt)^2
# RMSE
valrestuls$RMSE[valrestuls$Property == "alr_silt"] <- mean((valida$alr_Clay - pred_val_alrsilt)^2)^0.5
# ME
valrestuls$ME[valrestuls$Property == "alr_silt"] <- mean(valida$alr_Clay - pred_val_alrsilt)

## Residual variances
## layer A
residualvariances$layerA[residualvariances$Property == "alr_Silt"] <- var(valida$alr_Silt[valida$layer == 'A'] - pred_val_alrsilt[valida$layer == 'A'])
## layer B
residualvariances$layerB[residualvariances$Property == "alr_Silt"] <- var(valida$alr_Silt[valida$layer == 'B'] - pred_val_alrsilt[valida$layer == 'B'])
## layers A and B
residualvariances$layersAB[residualvariances$Property == "alr_Silt"] <- var(valida$alr_Silt - pred_val_alrsilt)
```

Save the table of the variance of the residuals into your working directory. This data  will be later used in the spatial analyses.
```{r eval = FALSE}
write.table(x = residualvariances, 
            file = "vnir_residual_variances.txt",
            sep = "\t",
            row.names = FALSE)
```

To asses the accuracies and precisions of the predictions (in the validation set) for particle-size distribution, we need to back-transform the additive log-ratio transformed variables to the original clay, silt and sand contents:
```{r eval = FALSE}
## Alr back-transformations
## Clay contents
valClay_alr <- 100 * exp(pred_val_alrclay)/(1 + exp(pred_val_alrclay) + exp(pred_val_alrsilt))
## Silt contents
valSilt_alr <- 100 * exp(pred_val_alrsilt)/(1 + exp(pred_val_alrclay) + exp(pred_val_alrsilt))
## Sand contents
valSand_alr <- 100 * 1/(1 + exp(pred_val_alrclay) + exp(pred_val_alrsilt))
```

Now we can compute the parameters to asses accuracies and precisions:
```{r eval = FALSE}
## Clay content 
## R2
valrestuls$R2[valrestuls$Property == "Clay"] <- (cor(valida$Clay, valClay_alr))^2
# RMSE
valrestuls$RMSE[valrestuls$Property == "Clay"] <- mean((valida$Clay - valClay_alr)^2)^0.5
# ME
valrestuls$ME[valrestuls$Property == "Clay"] <-  mean(valida$Clay - valClay_alr)

## Silt content 
## R2
valrestuls$R2[valrestuls$Property == "Silt"] <- (cor(valida$Silt, valSilt_alr))^2
# RMSE
valrestuls$RMSE[valrestuls$Property == "Silt"] <- mean((valida$Silt - valSilt_alr)^2)^0.5
# ME
valrestuls$ME[valrestuls$Property == "Silt"] <-  mean(valida$Silt - valSilt_alr)

## Sand content 
## R2
valrestuls$R2[valrestuls$Property == "Sand"] <- (cor(valida$Sand, valSand_alr))^2
# RMSE
valrestuls$RMSE[valrestuls$Property == "Sand"] <- mean((valida$Sand - valSand_alr)^2)^0.5
# ME
valrestuls$ME[valrestuls$Property == "Sand"] <-  mean(valida$Sand - valSand_alr)
```

Examine the `valrestuls` object...
```{r eval = FALSE}
valrestuls
```

## Property predictions in the prediction set
After validating the vis-NIR models we can apply them to the prediction set. 
We can start by creating a `data.frame` where the predictions will be stored. In this `data.frame` the predicted values will be stored under the following variable names: `Ca_spec`, `alr_Clay_spec` and `alr_Silt_spec`:
```{r eval = FALSE}
vnirpredictions <- data.frame(Ca_spec = rep(NA, nrow(pred)),
                              alr_Clay_spec = rep(NA, nrow(pred)),
                              alr_Silt_spec = rep(NA, nrow(pred)))

vnirpredictions <- data.frame(Ca_spec = rep(NA, nrow(pred)),
                              alr_Clay_spec = rep(NA, nrow(pred)),
                              alr_Silt_spec = rep(NA, nrow(pred)))

## Add additional relevant information from the original prediction set
vnirpredictions <- cbind(pred[,c("ID", 
                                 "POINT_X", 
                                 "POINT_Y",
                                 "set",
                                 "Ca",
                                 "Clay",
                                 "Silt",
                                 "Sand",
                                 "alr_Clay", 
                                 "alr_Silt")], 
                         vnirpredictions)

## Re-encode the set variable to "prediction"
vnirpredictions$set <- factor("prediction")
```

For exchangeable Ca^2+^ predictions...
```{r eval = FALSE}
# Predict Ca in the prediction set based on the optimized threshold
# distance for neighbor selection
sbl_ca_pred <- mbl(Yr = train$Ca, 
                   Xr = train$spc, 
                   Xu = pred$spc,
                   mblCtrl = ctrl,
                   group = train$samplegroup,
                   dissUsage = "none",
                   k.diss = best.kdiss.ca, 
                   k.range = kminmax,
                   pls.c = pls.f,
                   method = rmethod)
## get the predicted values and store them in nirpredictions
vnirpredictions$Ca_spec <- getPredictions(sbl_ca_pred)[,1]
```

For $alr(clay)$ predictions...
```{r eval = FALSE}
sbl_alrclay_pred <- mbl(Yr = train$alr_Clay, 
                        Xr = train$spc, 
                        Xu = pred$spc,
                        mblCtrl = ctrl,
                        group = train$samplegroup,
                        dissUsage = "none",
                        k.diss = best.kdiss.alrclay, 
                        k.range = kminmax,
                        pls.c = pls.f,
                        method = rmethod)
## get the predicted values and store them in nirpredictions
vnirpredictions$alr_Clay_spec <- getPredictions(sbl_alrclay_pred)[,1]
```

For $alr(silt)$ predictions...
```{r eval = FALSE}
sbl_alrsilt_pred <- mbl(Yr = train$alr_Silt, 
                        Xr = train$spc, 
                        Xu = pred$spc,
                        mblCtrl = ctrl,
                        group = train$samplegroup,
                        dissUsage = "none",
                        k.diss = best.kdiss.alrsilt, 
                        k.range = kminmax,
                        pls.c = pls.f,
                        method = rmethod)
## get the predicted values and store them in nirpredictions
vnirpredictions$alr_Silt_spec <- getPredictions(sbl_alrsilt_pred)[,1]
```

Examine the `vnirpredictions` object...
```{r eval = FALSE}
vnirpredictions
summary(vnirpredictions)
```
