# Prepare the vis-NIR augmented dataset

------------------------------------------------------------------------

Here we'll create the data that will be used for Spatial modelling. This dataset will contain 

* Nr: The arbitrary sample number.
* ID: The `factor` indicating the sample IDs.   
* POINT_X: The X (geographical) coordinate. 
* POINT_Y: The Y (geographical) coordinate.
* layer: A `factor` indicating the depth layer at which the sample was collected (A: 0-20 cm and B: 80-100 cm).
* set: A `factor` indicating whether the sample was used for vis-NIR calibrations (`train`), for vis-NIR predictions (`prediction`) or if it belongs to model's validation (`validation`). The samples labeled as validation are the same samples initially labeled as validation in the original dataset. 
* Ca: The exchangeable Calcium content in the sample ($mmol_{c}$ $kg^{−1}$, measured by conventional laboratory methods) 
* Clay: The percentage of clay contnet in the soil sample (measured by conventional laboratory methods). 
* Silt: The percentage of silt contnet in the soil sample (measured by conventional laboratory methods). 
* Sand: The percentage of sand contnet in the soil sample (measured by conventional laboratory methods). 
* alr_Clay: The additive log-ratio transformed clay contnets (measured by conventional laboratory methods).
* alr_Silt: The additive log-ratio transformed silt contnets (measured by conventional laboratory methods).
* Ca_spec: This is the vis-NIR augmented exchangeable Ca^2+^ contents.
* alr_Clay_spec: This is the vis-NIR augmented additive log-ratio transformed clay contnets.  
* alr_Silt_spec: This is the vis-NIR augmented additive log-ratio transformed silt contnets.  

For the vis-NIR augmented variables (alr_Clay_spc, alr_Silt_spc and Ca_spec) there are three classes of values:

* The values of the samples that are labeled as `train` come from the conventional laboratory methods (e.g. for Ca_spec the values of these samples for this variable are identical to the corresponding values in the variable Ca).

* The values of the samples that are labeled as `prediction` come from the predictions done with the respective vis-NIR model. 

* The values of the samples that are labeled as `validation` are treated as missing (i.e. `NA`s).

```{r, eval = FALSE}
## samples for the set "prediction"
vnirpredictions

## samples for the set "train"
vnirtrain <- train[ ,c("ID","POINT_X","POINT_Y","set", "Ca", "Clay", "Silt", "Sand", "alr_Clay","alr_Silt")]
vnirtrain$set <- factor("train") 
vnirtrain$Ca_spec <- vnirtrain$Ca
vnirtrain$alr_Clay_spec <- vnirtrain$alr_Clay
vnirtrain$alr_Silt_spec <- vnirtrain$alr_Silt

## samples for the set "validation"
vnirvalidation <- valida[ ,c("ID","POINT_X","POINT_Y","set", "Ca","Clay", "Silt", "Sand", "alr_Clay","alr_Silt")]
vnirvalidation$set <- factor(vnirvalidation$set)
vnirvalidation$Ca_spec <- NA
vnirvalidation$alr_Clay_spec <- NA
vnirvalidation$alr_Silt_spec <- NA
```

Now create a single `data.frame` containing the three data sets...
```{r, eval = FALSE}
vniraugmented <- rbind(vnirtrain, 
                       vnirpredictions,
                       vnirvalidation)

vniraugmented$layer <- factor(substr(vniraugmented$ID, 1, 1))

## Reorganize the variables
vniraugmented <- vniraugmented[,c("ID", 
                                  "POINT_X", 
                                  "POINT_Y", 
                                  "layer", 
                                  "set", 
                                  "Ca", 
                                  "Clay", 
                                  "Silt", 
                                  "Sand",
                                  "alr_Clay", 
                                  "alr_Silt", 
                                  "Ca_spec", 
                                  "alr_Clay_spec", 
                                  "alr_Silt_spec")]
```

Compute some statistics for the final data set...
```{r, eval = FALSE}
## Names of the properties
props <- c("Ca",
           "Clay",
           "Silt",
           "Sand",
           "alr_Clay",
           "alr_Silt",
           "Ca_spec",
           "alr_Clay_spec",
           "alr_Silt_spec")

## Compute the statistics: mean, standard deviation and 
##  the quantiles ("0%", "25%", "50%", "75%" and"100%")
statsprops <- aggregate(vniraugmented[, props],
                        by = list(set = vniraugmented$set,
                                  layer = vniraugmented$layer),
                        FUN = function(x){
                          c(mean = mean(as.matrix(x), na.rm = TRUE),
                            sd = sd(as.matrix(x), na.rm = TRUE),
                            quantile(x, na.rm = TRUE))
                        })

## Reorganize the object containing the results of the statistics
statsprops <- lapply(props, 
                     FUN = function(x, object, ids){
                       object <- cbind(object[,keep], 
                                       as.data.frame(statsquant[[x]]))
                       
                     }, 
                     object = statsprops,
                     ids = c("set", "layer"))
names(statsprops) <- props

statsprops <- do.call("rbind", statsprops)
statsprops$property <- gsub(".[0-9]", "", rownames(statsprops))
statsprops[is.na(statsprops)] <- NA

## Reorganize the order of the variables
statsprops <- statsprops[, c("set", 
                             "layer",
                             "property",
                             "mean",
                             "sd",
                             "0%",
                             "25%",
                             "50%",
                             "75%",
                             "100%")]

statsprops
```

Optionally, save this data in your working directory
```{r, eval = FALSE}
write.table(x = vniraugmented, 
            file = "vniraugmented.txt", 
            sep = "\t", 
            row.names = FALSE)
```
